Understanding the impacts of video-guided activities on parent-child interaction

### 2019-10-04 paper/manuscript.Rmd
clean up discussion and tweak figure

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4706"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))

d$MTLD = d$MTLD2
d$TTR = d$TTR2
d$types = d$types2
d$tokens = d$tokens2

e1ld <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD2),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(e1ld$gender)
#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
e1_parent_ed = table(e1ld$parent_ed)
```

@@

e1ja <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(Video),
         pja_length = pja_length/1000,
         cja_length = cja_length/1000,
         total_lja = total_lja/1000) # convert duration ms -> seconds
```

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))

d <- read.csv(paste(e2path,"exp2_conditions2.csv",sep=''))
d$MTLD = d$MTLD2
d$TTR = d$TTR2
d$types = d$types2
d$tokens = d$tokens2

e2data <- d %>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         TTR = as.numeric(TTR),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         video = as.factor(video))

@@

e2_gender = table(d$gender)
e2_ethnicity = table(d$ethnicity)
e2_parent_ed = table(d$parent_ed)
e2_12to18 = nrow(subset(d, age<1.5)) # wrong now that age is scaled
e2_18to24 = nrow(subset(d, age>=1.5))
```

@@

```{r, e1-lexdiv-regressions, echo=F, include=F}
require("rstanarm")
# get estimated coefficient and 95% CI from Bayesian regression
get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci = round(ci95, digits)
  names(ci) = c("95pLB","95pUB") # 95% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}

@@

We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

# Total number of bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, gender close

@@

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.08, 95% CI = [-2.18,0.07]
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")

@@

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot). 
Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "thank", "have", "which", and "school", while words that are most characteristic of the No Video condition include "ready", "on", "oh", "see", "going", "let", and "are".

@@

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

@@

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + theme(legend.position="none")

# multiplot(e1bids, e1tja, cols=2) # old Exp1
# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
multiplot(e1bids, e1tja, e2bids, e2tja_age, 
          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,3,4,4,4), nrow=2, byrow=T)) 
```

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable: 
after the Activity Video, parents used more words related to requests (e.g., "Can I have X? / Give me X. Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
There was lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]). 
There was no significant effect of age, nor a significant interaction.
The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

# Total number of bids
e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
summary(e2bids_m) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")

@@

We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other significant effects on parental bids for JA.

In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that older children participated in fewer episodes of JA. 
However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).

@@

# Total duration of passive joint attention.
e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2pjat_m) # age: est: -17.9 95% CI = [-33.1,-2.2] 
e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")

# Total duration of coordinated joint attention.
e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2cjat_m) # age: est: 35.3 95% CI = [-6.1,77.4] ns

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes revealed no significant effects.

In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), showing that older children had more episodes of passive JA with their caregiver.
The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]), revealing that older children spent more time in passive JA with their caregiver.
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "say", "does", "uhoh", "for", and "neigh".

@@

We were interested in how digital parenting advice alters parents' interactions with their children. 
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention. 
In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
In some cases--especially in older children--these bids were successful in increasing engagement. 
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity). 
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like").

@@

Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned). 
A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions. 
Providing materials may be critical for the success of activity suggestions. 
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research. 
A key goal for future research is to assess the generality of these findings across populations.

@@

<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens (significant in Exp. 1; numerical in Exp. 2), while the number of word types did not differ significantly across conditions. -->
<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4629"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
e1_parent_ed = table(d$parent_ed)
#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
d = read.csv("exp1_lexical_diversity_data.csv")

e1ld <- d %>%
  mutate(condition = factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(e1ld$gender)
```

@@

e1ja <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = langcog::scale(parent_ed, scale=TRUE),
         gender = as.factor(gender),
         Video = as.factor(Video),
         pja_length = pja_length/1000,
         cja_length = cja_length/1000,
         total_lja = total_lja/1000) # convert duration ms -> seconds
```

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
d = read.csv("exp2_lexical_diversity_data.csv")

e2data <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

@@

e2_gender = table(d$gender)
e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled
e2_18to24 = nrow(subset(d, Age>=1.5))
```

@@

```{r, e1-lexdiv-regressions, echo=F, include=F}
require("rstanarm")
# get estimated coefficient and 95% CI from Bayesian regression
get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  ci = round(c(ci95,ci89), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}

@@

We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

# Total number of bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, almost gender

@@

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.09, 95% CI = [-2.22,0.07] % report % posterior <0?
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")

@@

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot). 
Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that are most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.

@@

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.position="none")
  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

@@

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + 
  theme(legend.position="bottom", legend.text=element_text(size=9), 
        legend.margin=margin(0,0,5,0),
        legend.box.margin=margin(-10,-10,-5,-10))
  #theme(legend.position="none")

# multiplot(e1bids, e1tja, cols=2) # old Exp1
# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
multiplot(e1bids, e1tja, e2bids, e2tja_age, 
          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
```

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable: 
after the Activity Video, parents used more words related to requests (e.g., "Can I have X? / Give me X. Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
However, parents who watched an activity video also made more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]). 
The preregistered regression predicting the number of tokens used by parents revealed no effects. 
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

# Total number of bids
e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
summary(e2bids_m) # condition mean=3.1, 95%CI = [1.1, 5.0]
e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")

@@

We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf. int.: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other effects on parental bids for JA.

The regression predicting the number of episodes of JA revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
Older children also participated in fewer episodes of JA ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in fewer episodes of JA after an activity video.

@@

# Total duration of passive joint attention.
e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2pjat_m) # age: est: -17.97 95% CI = [-33.37,-2.41] 
e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")

# Total duration of coordinated joint attention.
e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2cjat_m) # age: est: 35.3 89% CI = [1.57,67.4] 
e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes found no notable effects.

Older children both engaged in more episodes of passive JA with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more total time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".

@@

We were interested in how digital parenting advice alters parents' interactions with their children. 
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention. 
In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
In some cases--especially in older children--these bids were successful in increasing engagement. 
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity). 
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like"), often asking about animal noises ("What does the X say?").

@@

Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned). 
A longer-term study would also address whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access to the materials needed to complete the suggested activities; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions. 
Providing materials may be critical for the success of activity suggestions. 
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research. 
A key goal for future research is to assess the generality of these findings across populations.

@@

<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens, while the number of word types did not differ significantly across conditions. -->
<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->
